---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rdev

<!-- badges: start -->
[![R-CMD-check](https://github.com/jabenninghoff/rdev/workflows/R-CMD-check/badge.svg)](https://github.com/jabenninghoff/rdev/actions)
[![lint](https://github.com/jabenninghoff/rdev/workflows/lint/badge.svg)](https://github.com/jabenninghoff/rdev/actions)
<!-- badges: end -->

## Overview

**`r packageDescription("rdev", fields = "Title")`:** `r packageDescription("rdev", fields = "Description")`

Feel free to use and/or fork this project!

## Installation

You can install the development version of rdev from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jabenninghoff/rdev")
```

Or using renv:

``` r
# install.packages("renv")
renv::install("jabenninghoff/rdev")
```

## Development

- Changelog: See "Changelog" or `NEWS.md`.
- Planned: [TODO](TODO.md)

## Creating Packages

rdev supports creation of new R packages following rdev conventions as well as new [R Analysis](https://jabenninghoff.github.io/rdev/articles/analysis-package-layout.html) packages. The typical setup workflow is:

1. Use `available::available()` to check package name
1. Create new base package using `create_github_repo()`
1. Manually set branch protection as needed (main: require status checks, linear history)
1. Add new package to GitHub Desktop
1. Commit to git `create_github_repo()`
1. Run `use_rdev_package()` within new project to add remaining templates and settings
1. Commit to git `use_rdev_package()`
1. Run either use_analysis_package() or usethis::use_pkgdown() for GitHub Pages
1. Commit to git
1. Edit DESCRIPTION and add a Title and Description
1. Update TODO.md, NEWS.md, README.Rmd, and DESCRIPTION as needed
1. Run `check_renv()`, `style_all()`, `lint_all()`, `ci()` to validate package
1. Commit to git and begin development

## GitHub Releases

rdev automates the workflow for creating GitHub releases along with updating GitHub pages for either standard R packages or R analysis packages, using the release notes format in NEWS.md. A typical development workflow is:

1. Bump version using `desc::desc_bump_version("dev")`, commit to new feature branch
1. *Write all the things*
1. Update the release notes for the new version in NEWS.md, following the conventions described in `get_release()`
1. Finalize the release and merge all changes to git
1. Run `stage_release()` to create a new pull request on GitHub using details derived from NEWS.md, including updating the README and GitHub pages
1. After the pull request has been reviewed and passes all required status checks, accept the staged release with `merge_release()`, which merges the pull request, cleans up branches, and publishes a new GitHub release

Feature branches can be merged without starting a new release; `stage_release()` just requires that everything is committed, including new release notes in NEWS.md before running. When ready to release, `stage_release()` will use the existing branch if on a feature branch, and create a new release branch if on the default.

## Examples

For my workflow, I typically check renv when I start:

```{r check_renv}
library(rdev)

check_renv()
```

I also have a `ci()` function to run all my continuous integration tests locally:

```{r ci}
ci()
```
