---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rdev

<!-- badges: start -->
[![R-CMD-check](https://github.com/jabenninghoff/rdev/workflows/R-CMD-check/badge.svg)](https://github.com/jabenninghoff/rdev/actions)
[![lint](https://github.com/jabenninghoff/rdev/workflows/lint/badge.svg)](https://github.com/jabenninghoff/rdev/actions)
<!-- badges: end -->

## Overview

**`r packageDescription("rdev", fields = "Title")`:** `r packageDescription("rdev", fields = "Description")`

Feel free to use and/or fork this project!

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jabenninghoff/rdev")
```

Or using renv:

``` r
# install.packages("renv")
renv::install("jabenninghoff/rdev")
```

## Development

- Changelog: See "Changelog" or `NEWS.md`.
- Planned: [TODO](TODO.md)

## Creating Packages

rdev supports creation of new R packages following rdev conventions as well as new [R Analysis](https://jabenninghoff.github.io/rdev/articles/analysis-package-layout.html) packages. The typical setup workflow is:

1. Use `available::available()` to check package name
1. Create new base package using `create_github_repo()`
1. Manually set branch protection as needed (main: require status checks, linear history)
1. Add new package to GitHub Desktop
1. Commit to git `create_github_repo()`
1. Run `use_rdev_package()` within new project to add remaining templates and settings
1. Commit to git `use_rdev_package()`
1. Run either use_analysis_package() or usethis::use_pkgdown() for GitHub Pages
1. Commit to git
1. Edit DESCRIPTION and add a Title and Description
1. Update TODO.md, NEWS.md, README.Rmd, and DESCRIPTION as needed
1. Run `check_renv()`, `style_all()`, `lint_all()`, `ci()` to validate package
1. Commit to git and begin development

## Examples

For my workflow, I typically check renv when I start:

```{r check_renv}
library(rdev)

check_renv()
```

I also have a `ci()` function to run all my continuous integration tests locally:

```{r ci}
ci()
```
