---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rdev

<!-- badges: start -->
[![R-CMD-check](https://github.com/jabenninghoff/rdev/workflows/R-CMD-check/badge.svg)](https://github.com/jabenninghoff/rdev/actions)
<!-- badges: end -->

## Overview

**`r packageDescription("rdev", fields = "Title")`:** `r packageDescription("rdev", fields = "Description")`

Feel free to use and/or fork this project!

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jabenninghoff/rdev")
```

Or using renv:

``` r
# install.packages("renv")
renv::install("jabenninghoff/rdev")
```

## Development

- Changelog: See "Changelog" or `NEWS.md`.
- Planned: [TODO](TODO.md)

## Examples

For my workflow, I typically check renv when I start:

```{r example}
library(rdev)

check_renv()
```

I also have a `ci()` function to run all my continuous integration tests locally:

```{r}
ci()
```
