---
title: "Style Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Style Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The R Style Guide describes the rdev style conventions, along with automated checks
([styler](https://styler.r-lib.org) and [lintr](https://lintr.r-lib.org)). The rdev R Style Guide
incorporates both the [Tidyverse Style Guide](https://style.tidyverse.org) and
[Google's R Style Guide](https://google.github.io/styleguide/Rguide.html).

## rdev conventions

rdev uses a mix of Google and tidyverse conventions.

### Naming conventions

rdev follows the tidyverse naming convention of `snake_case`.

### Right-hand assignment

rdev follows Google's style guide, and does not use right-hand assignment.

### Returns

rdev typically uses implicit returns unless needed for flow control or to construct a specific
return structure.

### Qualifying namespaces

Use of `@import` and `@importFrom` are discouraged, instead using `::` in functions defined in `R/`.
An exception is infix functions (`%name%`), which are always imported, using roxygen `@importFrom`.
Within R and Quarto Notebooks, use of `library()` is encouraged for readability.

### Package-level documentation

rdev package documentation lives in `R/package.R`.

Additionally, use of base R is encouraged within functions defined in `R/` (to control
dependencies), where tidyverse R is encouraged within notebooks for readability.

R Markdown documents should generally wrap at the same width as code, with exceptions for the R
Notebook 'description line' (the first non-blank line in the body), and long hyperlinks.

## styler

The rdev package implements [styler](https://styler.r-lib.org) using the styler defaults, with
permanent caching enabled (`options(styler.cache_root = "styler-perm")`). The `style_all()` function
applies the tidyverse style to all R and Quarto files (`R`, `Rprofile`, `Rmd`, `Rnw`, `qmd`) in the
package directory structure.

## lintr


The `lint_all()` function lints all R and Quarto files (`R`, `Rmd`, `qmd`, `Rnw`, `Rhtml`, `Rpres`,
`Rrst`, `Rtex`, `Rtxt`) with [lintr](https://lintr.r-lib.org) using an opinionated
configuration (`.lintr`):

```r
linters: linters_with_tags(
    tags = NULL,
    implicit_integer_linter = NULL,
    line_length_linter(100),
    missing_package_linter = NULL,
    namespace_linter = NULL,
    nonportable_path_linter = NULL,
    paste_linter(allow_file_path = "always"),
    todo_comment_linter = NULL,
    undesirable_function_linter(
      within(all_undesirable_functions, rm(ifelse, library, require, structure))
    ),
    undesirable_operator_linter(all_undesirable_operators),
    unnecessary_concatenation_linter(allow_single_expression = FALSE),
    unused_import_linter(
      except_packages = c("bit64", "data.table", "tidyverse", pkgload::pkg_name("."))
    )
  )
```

These settings were deliberately chosen to meet specific goals:

### Use all linters

```r
linters: linters_with_tags(
    tags = NULL,
```

This selects all linters, including the new
[Google linters](https://lintr.r-lib.org/news/index.html#google-linters-3-0-0). By selecting all
linters, not just the defaults, this forces evaluation of new linters as they are added to lintr.
Specific linters are disabled or configured per rdev style.

### Allow implicit integers

```r
    implicit_integer_linter = NULL,
```

The implicit integer linter checks that integers are explicitly typed using the form `1L`. Again,
while this is safer, implicit integers are common practice, including in the output of `dput()`:

```{r implicit_integer}
dput(character(0L))
```

### Set line length

```r
    line_length_linter(100),
```

A line length of 100 is a reasonable width when working in the RStudio IDE on a laptop.

### Use renv for missing packages

```r
    missing_package_linter = NULL,
    namespace_linter = NULL,
```

The missing package linter and the namespace linter both check for packages referenced in code that
are not installed. rdev uses [renv](https://rstudio.github.io/renv/) to manage packages, which does
a better job of detecting missing packages, including not complaining when the current package
(`"."`) is not installed.

### Allow non-portable paths

```r
    nonportable_path_linter = NULL,
    paste_linter(allow_file_path = "always"),
```

The non-portable path linter generates too many false positives, including calls to
[fs](https://fs.r-lib.org), which essentially makes UNIX-style paths portable across operating
systems. Similarly, the `allow_file_path` default option of `"double_slash"` generates false
positives when used with fs.

### Allow TODO comments

```r
    todo_comment_linter = NULL,
```

rdev conventions encourage use of `# TODO:` comments as a convenient way of identifying needed or
planned updates inline.

### Disallow almost all undesirable functions and operators

```r
    undesirable_function_linter(
      within(all_undesirable_functions, rm(ifelse, library, require, structure))
    ),
    undesirable_operator_linter(all_undesirable_operators),
```

Enable all undesirable functions and operators, not just the defaults, except for `ifelse()` which
is more succinct than an `if`/`else` block, `library()`, `require()`, and `structure()`. Use of
`require()` within `.Rprofile` and `library()` within R Markdown documents is an appropriate and
common practice, although neither should be used within package code. `structure()` is useful for
comparing test results to values generated with `dput()`.

### Enforce strict unnecessary concatenation

```r
    unnecessary_concatenation_linter(allow_single_expression = FALSE),
```

Enforce the stricter version of the unnecessary concatenation linter.

### Verify imported packages are used

```r
    unused_import_linter(
      except_packages = c("bit64", "data.table", "tidyverse", pkgload::pkg_name("."))
    )
  )
```

Verify that imported packages are used, except for packages that are attached for their side
effects, and the current package (to support package development).
