---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {{{ repo }}}

<!-- badges: start -->
[![R-CMD-check](https://github.com/{{{ username }}}/{{{ repo }}}/workflows/R-CMD-check/badge.svg)](https://github.com/{{{ username }}}/{{{ repo }}}/actions)
[![lint](https://github.com/{{{ username }}}/{{{ repo }}}/workflows/lint/badge.svg)](https://github.com/{{{ username }}}/{{{ repo }}}/actions)
<!-- badges: end -->

## Overview

**`r desc::desc_get_field("Title")`:** `r desc::desc_get_field("Description")`

Feel free to use and/or fork this project!

## Installation

You can install the development version of {{{ repo }}} from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("{{{ username }}}/{{{ repo }}}")
```

Or using renv:

``` r
# install.packages("renv")
renv::install("{{{ username }}}/{{{ repo }}}")
```

## Development

- Changelog: See "Changelog" or `NEWS.md`.
- Planned: [TODO](TODO.md)

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
#| label: example
# basic example code
```
