---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
library(rdev)
library(fs)
library(dplyr)
library(purrr)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {{{ repo }}}

<!-- badges: start -->
[![R-CMD-check](https://github.com/{{{ username }}}/{{{ repo }}}/workflows/R-CMD-check/badge.svg)](https://github.com/{{{ username }}}/{{{ repo }}}/actions)
[![lint](https://github.com/{{{ username }}}/{{{ repo }}}/workflows/lint/badge.svg)](https://github.com/{{{ username }}}/{{{ repo }}}/actions)
<!-- badges: end -->

## Overview

**`r desc::desc_get_field("Title")`:** `r desc::desc_get_field("Description")`

Feel free to use and/or fork this project!

## Notebooks

Notebooks in this package:

```{r notebooks, echo = FALSE, results = 'asis'}
notebooks <- dir_ls("analysis", glob = "*.Rmd") |>
  map_dfr(rmd_metadata) |>
  mutate(bullet = paste0("- [", title, "](", url, ") (", date, "): ", description)) |>
  pull(bullet)

writeLines(notebooks)
```

## Installation

You can install the development version of {{{ repo }}} from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("{{{ username }}}/{{{ repo }}}")
```

Or using renv:

``` r
# install.packages("renv")
renv::install("{{{ username }}}/{{{ repo }}}")
```

## Development

- Changelog: See "Changelog" or `NEWS.md`.
- Planned: [TODO](TODO.md)
